\documentclass[11pt]{article}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
\title{GFW: Protection or censorship?\\ \large A brief overview on China's Great Firewall system}
\author{Hengyi Li}
\newcommand{\name}{Hengyi Li}
\usepackage[paper=letterpaper, margin=1in, headheight=13.6pt]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\cfoot{Page \thepage}

\usepackage[parfill]{parskip}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{upquote}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{xeCJK}

\begin{document}
\maketitle
\bibliographystyle{mla}
\section{Introduction}

The Internet has come a long way today. As a bridge for the flow of information,
it carries the thoughts, ideas, opinions and needs of all people. However,
because of the value attributes of information, the flow of information may
inadvertently touch the interests of certain people or groups. This may lead to
theft by criminals, or it may be a threat to national security, but in any case,
the network firewall has been built as a result. In China, there also exists
such a wall, which is not only able to defend against cyber-attacks from outside
the country, but at the same time, and most importantly, prevents the flow of
network traffic from within the country to outside the country. This is the
subject of this article - The Great Firewall.

\section{Background}
Great Firewall (hereinafter referred to as GFW) is a traffic censorship and
attack defense system based on Cisco's intrusion detection system \cite{CISCO}.
This defense system combines active and passive detection capabilities to censor
China's Internet traffic \cite{DetectBlockShadowSocks}. As far as we know from
our testing, the system is running on IPV4, but we have no way of knowing if the
system is compatible with IPV6 as well. The main reason for this is that IPV6 is
not very popular in China, and even if we could ask the carriers to enable it,
they would not be very willing to do so for security reasons, and it would
require a series of very complicated procedures to complete.

What's worse, the GFW is still a black box system for outsiders and researchers,
and the existence of the system is not recognized at the national level, and
there is no official documentation about the system. All research into the
system is currently in the ``poke around and see what happend'' phase, so most
of the results and findings below come from community organizations and web
forum members. We would like to thank the members and contributors of the gfw.
repot \cite{GFWReport} website for providing a wealth of documentation and
experimental data without which we would not have been able to gain such a deep
understanding of GFW. In order to begin to understand how the GFW network in
China works, we need to first understand the composition of the network
structure in China, which has a huge difference with here in the U.S.

Now, China's Internet is divided into two parts, the national intranet and the
international network. Since 2013, China's internet technology companies have
grown and expanded into a wide range of industries, creating an ecosystem of
apps for every need and an internal loop. For example, we have Bilibili, which
is the Chinese version of Youtube. We have Baidu, which is the Chinese version
of Google We have Weibo to replace the Twitter, we have WeChat to replace the
Facebook and WhatsApp and the alternate to Apple Pay/Google Pay and a series of
other payment tools in China is Alipay and WeChat Pay. Every application you
know, we have a alternative version and it's optimized just for Chinese market.
Everything we need is in the intranet, so most of people choose to live in a
environment like this. But what it brings is the information cocoon. Because the
Chinese language is so special, learning English can be much more difficult for
Chinese people than it is for Americans learning Spanish. The rising cost of
learning means that most people won't bother to learn the language, and thus the
breadth of the information stream they receive on a daily basis will become
narrower and narrower. Unfortunately, because of the speciality of the Chinese
language and its strong historical and cultural ties, the Chinese language media
is mostly limited to the territory of China and the GFW exacerbates this
situation by making it more difficult to access foreign media.

That's not what we want, and it's not what we want to see the Internet will
become. Information should flow freely, and anyone should be able to access as
much information as they want without compromising national security.
Communication between people should not be hindered by the advent of technology,
and unfortunately, GFW is one of the technologies that builds barriers. It
didn't come about by accident, but because of a combination of historical
legacies and improvisational decisions. For the sake of safety, we will only
discuss its technical aspects here, and we would start by discussing the network
architecture legacy.

\section{China's internet architecture}

Because of the limited number of IPv4 addresses and China's large population
base, China is facing the problem of running out of IPv4 addresses earlier than
other countries in the world. At that time, IPv6 protocol had not yet been
proposed. As a response, the three major carriers in China coincidentally chose
carrier-grade NAT when setting up their networks, which effectively reduced the
use of public IPv4 addresses by converting a large number of private IPv4
addresses into a small number of public IPv4 addresses \cite{CISCONAT}.

Therefore, the Chinese network architecture now becomes based on NAT technology.
Normal people will not have a public IP address, but all private IP
addresses provided by ISPs, and, because China's Internet, cell phone and TV
services are monopolized by three state-owned companies, China Mobile, China
Telecom and China Unicom. The network architecture has become an onion-like NAT
bridging model. Because of this bridging model, network providers can isolate
intranet access requests from international access requests very easily. In
order to meet the demand for international access, China has set up
international line servers in three major cities, Beijing, Shanghai and
Guangzhou, and deployed GFWs on them, which can be interpreted as network
outbound customs, so that all outbound traffic must pass through the servers in
one of the three cities and go through the GFWs' scrutinizing process before
going out of the country \cite{GlobalNetServer}.

Let's simulate a situation for better understanding. Suppose we have a laptop in
Chengdu trying to access the ucdavis.edu website, then the request will go
through the following process
\begin{align*} &Laptop \rightarrow \text{Home Router} \rightarrow
\text{Community Server} \rightarrow \text{Distinct Server}\\ &\rightarrow
\text{City Datacenter} \rightarrow \text{Province Datacenter} \rightarrow
\text{Guangzhou Datacenter}\\ &\rightarrow \text{GFW server} \rightarrow
\text{UCDavis server} \end{align*}
As you can see, it takes a long way from Chengdu to connect to the server at UCDavis.
At the same time, keep in mind that each hop is accomplished by IP conversion
through NAT layer by layer. And in the final pass through the GFW is also like
going through customs, the GFW will review the legal compliance of the
destination address, and whether it is on the blacklist. If the address is on
GFW's blacklist (e.g. Youtube.com), GFW will reject the connection and send a
reset request to both parties or wait until the connection times out. I'll
discuss GFW's blocking patterns further in the next section.

\section{GFW's Working Principle}

\newpage
\bibliography{GFW-Brief.bib}
\begin{thebibliography}{9}
\bibitem{DetectBlockShadowSocks} Anonymous, et al. \textit{"How China Detects
and Blocks Shadowsocks."} GFW Report, 29 Dec. 2019, gfw.
report/blog/gfw\_shadowsocks. Accessed 11 Jan. 2024.

	\bibitem{CISCONAT} Cisco.com. "Carrier Grade Network Address Translation."
	\textit{Information About Carrier Grade Network Address Translation}, www.cisco.com/c/en/us/td/docs/routers
	en/us/td/docs/routers/ios/config/17-x/ip-addressing/b-ip-addressing/m\_iadnat-cgn.pdf. Accessed 11 Jan. 2024

	\bibitem{GFWReport} Great Firewall Report. \textit{"Great Firewall Report."}
	Great Firewall Repor, Dec. 2019, gfw.report. Accessed 11 Jan. 2024.

	\bibitem{CISCO}
	Schaack, Beth Van. \textit{"China's Golden Shield: Is Cisco Systems Complicit?"} Center
	for Internet and Society, 24 Mar. 2015, cyberlaw.stanford.edu/blog/2015/03/china\%E2\%80\%99s-golden-shield-cisco-systems-complicit.
	Accessed 11 Jan. 2024.

	\bibitem{GlobalNetServer}
	聿纾. \textit{"国内主流网络运营商国际连接线路简谈."} 知乎专栏, zhuanlan.zhihu.com/p/64467370.

\end{thebibliography}
\end{document}
